Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-07-26 ms.tex
Fix capitalization
Shorten overblown sentence
Spelling

A laser interferometer senses \acp{GW} by transducing differential changes in arm length to a digitized photocurrent time series. In the angular frequency domain, a single detector's observation $X_i(\omega)$ is
%
\begin{equation}\label{eq:signal-model}
	x_i (\omega) = h_i (\omega; \boldsymbol\theta) + n_i (\omega),
\end{equation}
%
where $h_i (\omega; \boldsymbol\theta)$ is the \ac{GW} signal receied by detector $i$, given a parameter vector $\boldsymbol\theta$ that describes the \ac{GW} source, and $n_i (\omega)$ is that detector's \ac{WSS} Gaussian noise with \ac{PSD} $S_i(\omega)$. We shall denote the combined observation from a network of detectors as $\mathbf x (\omega) \equiv \{x_i (\omega)\}_i$.

>>>>

In the frequency domain, the data recorded by a single \ac{GW} interferometer are
%
\begin{equation}\label{eq:signal-model}
	x_i (\omega) = h_i (\omega; \boldsymbol\theta) + n_i (\omega),
\end{equation}
%
where $h_i (\omega; \boldsymbol\theta)$ is the \ac{GW} signal received by detector $i$, given a parameter vector $\boldsymbol\theta$ that describes the \ac{GW} source, and $n_i (\omega)$ is that detector's \ac{WSS} Gaussian noise with \ac{PSD} $S_i(\omega)$. We shall denote the combined observation from a network of detectors as $\mathbf x (\omega) \equiv \{x_i (\omega)\}_i$.
